\doctitle

### 2023-05-04 msr3-theory.tex
Add PIKN chapter; Add todos across the doc
Add sensitivity+scalability analyses and covid example
Address multiple TODO items in MSR3 chapter

%gives the problem structure used in the design of our
%numerical solution method. 
%Specifically, we design a 
%(PGD) %prox gradient 
%method 
%for solving this problem (see Section \ref{sec:pgd}). For this we must show that the function $u_\emu$
%is continuously differentiable with Lipschitz continuous gradient.

%\section{Prox Gradient Descent}
\subsection{Proximal Gradient Descent for \texorpdfstring{$\uemu\tbg + R\tbg+\del_{\Rqp}(\tgam)$}{}} 
\label{sec:pgd}

@@

\begin{algorithm}[H]
\SetAlgoLined
{\bf Initialize:} 
$\theta\in(0,1),\ \tau\in(0,1)$,
$\eta>0,\ \mu>0$, $\eps_{\mbox{\tiny Tol}}\ge 0$
$k=0$, $t_0>0$, $\bw^{0}=(\tbeta^0,\tgam^0)\in \Rp\times\R^q_+$
with $\inf\Phi_\emu <\Phi_\emu(\bw^0)$, 
$\gammax>\tgam^0$, 
$w^0=\prox_{t_0\tR}(\bw^{0}-t_0\nabla u_\emu(\bw^0))$.
%$, \ \eta_{Tol}\ge\eta_0>0,\ \mu_0\ge \mu_{Tol}>0$.
\\
\While{{\small $\norm{w^k-\bw^k}>\eps_{\mbox{\tiny Tol}}$
and $\gam^k\le\gammax$}}{\small\smallskip
\begin{enumerate}
\item[(i)] $t_{k+1}=\max\lset{t}{
\begin{aligned}&s\in\bW,\, t=t_0\theta^s,\ 
w=\prox_{t\tR}(w^k-t\nabla u_\emu(w^k))\\ &
\phi(w)
\le \phi(w^k)-\tau t\norm{w^k-w}^2
\end{aligned}}$.
\item[(ii)] $\bw^{k+1}=w^{k}$
\item[]$w^{k+1}=\prox_{t_{k+1}\tR}(w^k-t_{k+1}\nabla u_\emu(w^k))$
\item[]$k=k+1$
\end{enumerate}
}
\smallskip
\caption{\label{alg:pgd with bt}Proximal Gradient Descent 
fo $\Phi_\emu$ with Backtracking}
\end{algorithm}
\medskip

@@

%\begin{figure}[t]
%    \centering
%    \includegraphics[width=\textwidth]{Images/intuition_current.pdf}
%    \caption{Proximal Gradient Descent (PGD) takes an order of magnitude fewer iterations to converge when optimizing a value function instead of the original likelihood, because SR3-relaxation improves the conditioning of the problem, which results in a more spherical level-sets. This effect persists for both quadratic convex (first row) and non-convex components (second row) of the likelihood. The effect is stronger for  minima near the boundary of the constraint region 
%    (bottom-left panel).}
%    \label{fig:geometric_intuition_sr3}
%\end{figure}

\subsection{The Smoothness of \texorpdfstring{$u_\emu$}{}}\label{sec:smoothness}
We investigate the relationship between the problems \eqref{eq:lme_loss_original_in_x}
and \eqref{eq:relax2}, the existence of solutions to 
 \eqref{eq:relax2}, and the properties of the function $\uemu$ and its derivative.
%We begin with an examination of the function $\LL$
%and 
%The first step is to understand the role of the parameter $\blam$.

@@

\subsubsection{The Lipschitz Continuity of \texorpdfstring{$\nabla \uemu\tbg$}{}}

@@

\subsection{Convergence of the PGD Algorithm for \texorpdfstring{$\Phi_\emu$}{}}
\label{sec:convergence pgd}

>>>>

In this section we provide a 
theoretical justification for the algorithmic approach to the solution
of the marginalized maximum likelihood estimation problems presented
in~\cite{aravkin2022jimtheory} as well as in Section~\ref{sec:MSR3}. The approach is motivated by the sparse relaxed regularization regression (SR3) strategy
developed in \cite{Zheng2019SR3}. While the analysis of~\cite{Zheng2019SR3} relies on the least squares data-fitting term,
here we develop the algorithmic design and analysis required for the nonlinear and nonconvex LME extension.

This section proceeds as follows. 
% Section 3
We study the relaxation strategy defined in~\eqref{eq:relax} where the the relaxation depends on a decoupling
parameter $\eta$ and log-barrier smoothing parameter $\mu$. In particular, we introduce
the optimal value function $\uemu$~\eqref{eq:value_function_definition} 
used to exploit the decoupling of the likelihood
function from the sparsity regularizer. Here $\uemu$ is obtained by partially minimizing
the decoupled variables in the likelihood while keeping those in the regularizer fixed. 
% Section 4
Section~\ref{sec:pgd} introduces the MSR3 algorithm
as the PGD algorithm 
applied to the sum of $\uemu$ and the sparsity regularizer. 
A brief discussion the basic assumptions typically required
for establishing the viability of the PGD algorithm for this formulation is given.
% Section 5
Section~\ref{sec:smoothness} is the theoretical core of the work. In this section
we show that the optimal value function function $\uemu$ satisfies the properties
necessary for the application of the PGD algorithm. 
In particular, we establish the Lipschitz continuity of $\nabla \uemu$ 
(Lemma \ref{lem:grad u lip}). 
% Section 6
The convergence results for MSR3 are presented in Section~\ref{sec:convergence pgd}
for fixed values of $\eta$ and $\mu$.
% Section 7
In Section~\ref{sec:hybrid alg} we address the key issues surrounding the initialization
of the coupling and smoothing parameters $\eta$ and $\mu$ when only approximate
values for $\uemu$ and $\nabla \uemu$ are known. Here we appeal to both
variable metric ideas as well as properties of the interior point algorithm.

\subsection{Proximal Gradient Descent for the Regularized Value Function} 
\label{sec:pgd}

@@

\begin{algorithm}[ht]
\SetAlgoLined
{\bf Initialize:} 
$\theta\in(0,1),\ \tau\in(0,1)$,
$\eta>0,\ \mu>0$, $\eps_{\mbox{\tiny Tol}}\ge 0$
$k=0$, $t_0>0$, $\bw^{0}=(\tbeta^0,\tgam^0)\in \Rp\times\R^q_+$
with $\inf\Phi_\emu <\Phi_\emu(\bw^0)$, 
$\gammax>\tgam^0$, 
$w^0=\prox_{t_0\tR}(\bw^{0}-t_0\nabla u_\emu(\bw^0))$.
%$, \ \eta_{Tol}\ge\eta_0>0,\ \mu_0\ge \mu_{Tol}>0$.
\\
\While{{\small $\norm{w^k-\bw^k}>\eps_{\mbox{\tiny Tol}}$
and $\gam^k\le\gammax$}}{\small\smallskip
\begin{enumerate}
\item[(i)] $t_{k+1}=\max\lset{t}{
\begin{aligned}&s\in\bW,\, t=t_0\theta^s,\ 
w=\prox_{t\tR}(w^k-t\nabla u_\emu(w^k))\\ &
\phi(w)
\le \phi(w^k)-\tau t\norm{w^k-w}^2
\end{aligned}}$.
\item[(ii)] $\bw^{k+1}=w^{k}$
\item[]$w^{k+1}=\prox_{t_{k+1}\tR}(w^k-t_{k+1}\nabla u_\emu(w^k))$
\item[]$k=k+1$
\end{enumerate}
}
\smallskip
\caption{\label{alg:pgd with bt}Proximal Gradient Descent 
fo $\Phi_\emu$ with Backtracking}
\end{algorithm}
\medskip

@@

%\begin{figure}[ht]
%    \centering
%    \includegraphics[width=\textwidth]{Images/intuition_current.pdf}
%    \caption{Proximal Gradient Descent (PGD) takes an order of magnitude fewer iterations to converge when optimizing a value function instead of the original likelihood, because SR3-relaxation improves the conditioning of the problem, which results in a more spherical level-sets. This effect persists for both quadratic convex (first row) and non-convex components (second row) of the likelihood. The effect is stronger for  minima near the boundary of the constraint region 
%    (bottom-left panel).}
%    \label{fig:geometric_intuition_sr3}
%\end{figure}

%\subsection{The Smoothness of \texorpdfstring{$u_\emu$}{}}
\subsection{The Smoothness of the Value Function}
\label{sec:smoothness}
We investigate the relationship between the problems \eqref{eq:lme_loss_original_in_x}
and \eqref{eq:relax2}, the existence of solutions to 
 \eqref{eq:relax2}, and the properties of the function $\uemu$ and its derivative.
%We begin with an examination of the function $\LL$
%and 
%The first step is to understand the role of the parameter $\blam$.

@@

%\subsubsection{The Lipschitz Continuity of \texorpdfstring{$\nabla \uemu\tbg$}{}}
\subsubsection{The Lipschitz Continuity of the Gradient of the Value Function}

@@

\subsection{Convergence of the PGD Algorithm for Regularized MSR3 Likelihood}
\label{sec:convergence pgd}

### 2023-05-04 msr3.tex
Address multiple TODO items in MSR3 chapter

\edit{Rewrite the MSR3 abstract into a summary of whole work with citations}
Linear Mixed-Effects (LME) models are a fundamental tool for modeling correlated data, 
including cohort studies, longitudinal data analysis, and meta-analysis.  Design and analysis of variable selection methods for LMEs is more difficult than for linear regression because LME models are nonlinear. In this work we 
propose a relaxation strategy and optimization methods that enable a wide range of variable selection methods for LMEs using both convex and nonconvex regularizers, including  $\ell_1$, Adaptive-$\ell_1$, SCAD, and $\ell_0$. 
The computational framework only requires the proximal operator for each regularizer to be available, and the implementation is available in an open source \texttt{python} package \texttt{pysr3}, consistent 
with the \texttt{sklearn} standard. 
The numerical results on simulated data sets indicate that the proposed strategy improves on the state of the art for both accuracy and compute time. 
The variable selection techniques are also validated on a real example using a data set on bullying victimization.

@@

%Roadmap
We begin in Section \ref{sec:LMEM} by giving a precise description of the LME
model and set the notation for the remainder of the paper. 
This is followed by a brief discussion of prior work on LMEs.
In Section \ref{sec:pgd_methods} we present our algorithms for the LME model 
starting with the naive PGD algorithm. This is followed by a description of the 
variable splitting technique used in \cite{Zheng2019SR3} to incorporate global 
variation information on the likelihood function into the direction finding subproblem
for the PGD algorithm. 
%This lays the foundation for the MSR3 algorithm. 
Next we tackle the problem of how to approximate the 
resulting optimal value function $u_\eta$ and its gradient where $\eta>0$ is the 
decoupling parameter. As noted, this is done using variable metric techniques and 
and interior point technology. We conclude Section \ref{sec:pgd_methods} 
with a discussion of the
MSR3 and MSR3-fast algorithms. In Section \ref{sec:applications} we discuss how
the underlying algorithmic parameters are set and test the algorithm on both 
simulated problems and a problem with real data. The paper is concluded in
Section \ref{sec:discussion} with a brief discussion of the contributions.

\edit{Add a paragraph summarizing the theory paper}
\edit{Add a paragraph summarizing software paper}

@@

@@

 A popular nonconvex regularizer used for feature selection is smoothed clipped absolute deviation (SCAD)~\cite{Fan2001}. 
 %The (non-smoothed) clipped absolute deviation penalty is depicted in panel (d) of Figure~\ref{fig:regularizers}.
% , and the algebraic forms for both CAD and SCAD are given in the appendix. 
% which acts on the first derivative of the penalty function $p_\lambda(\theta)$:
 %  \eq{
  % 		p'_{\lambda}(|\theta|) = \lambda\left\{\ind{\theta \leq \lambda} +  \frac{(a\lambda - \theta)_+}{(a-1)\lambda}\ind{\theta - \lambda} \right\}
  % }
The adaptation of the SCAD penalty to select both fixed and random features in 
linear mixed models was developed by \cite{Fan2012}. SCAD was also used by \cite{chen2015inference} for selecting fixed effects and establishing the existence of random effects in ANOVA-type models. Finally, \cite{Ghosh2018} studied SCAD regularization for selecting mean effects in high-dimensional genomics problems.

To better compare methods, we need to consider the tuning of the regularization parameter 
$\lambda$. 
The output of a shrinkage model critically depends on the tuning parameter 
$\lambda$. The entire range of $\lambda$ values is captured 
by the notion of a ``$\lambda$-path in the model space'', with  the best parameter and the final model chosen using information criteria. According to \cite{Muller2013}, the most widely used information criterion is the marginal AIC criterion (\cite{Vaida2005}),
 \(  AIC := 2\LL(\hat{\theta}) + 2\alpha_n(p+q)\), 
  where $\hat\theta$ includes all the estimated parameters $(\beta, \Gamma)$, and $\alpha_n := n(n-p-q-1)$ for the finite sample case (\cite{Sugiura1978}). 
  %As discussed by \cite{Fang2011}, AIC is asymptotically equivalent to leave-one-out cross-validation, so it can be used for choosing between a finite number of models. AIC, however, is also known to be positively-biased (\cite{Ibrahim2011}). 
  Alternatively, LASSO-type methods (\cite{Krishna2008, Ibrahim2011}) use a BIC-type information criterion,  \(BIC := 2\LL(\hat{\theta}) + \log(n)(p+q)\).
BIC performs well in practice, but does not have theoretical guarantees~(\cite{schelldorfer2011estimation}).
  %One can refer to \cite{Muller2013, Buscemi2019Survey} for a detailed overview of different feature selection approaches.

  \edit{Add more ICs, e.g. Muller}

@@

Our focus is on the optimal value function $\uemu$ which captures global 
variational information about the function $\LL$ over its domain.
We show that $\uemu$ has a locally Lipschitz continuous gradient
and that the evaluation of $\uemu$ and $\nabla \uemu$ is accomplished
by optimizing a well conditioned strongly convex function. This
allows us to apply the PGD algorithm to the function $\uemu$ rather than
the function $\LL$. Our numerical studies show that the global information 
captured by $\uemu$ significantly improves both the accuracy of the solution
obtained and the overall numerical efficiency of the algorithm.

\edit{Connect this paragraph to the theory block}

To motivate the reader, the theoretical results that support the design of Algorithm \ref{alg:MSR3} go as follows. The existence of solutions for the problem~(\ref{eq:value_function_definition}) for any positive $\mu$ is shown in \cite[Theorem 5]{Theory1}, and the convergence of solutions to the MSR3 solution as $\mu\downarrow 0$ is shown in~\cite[Theorem 7]{Theory1}.  
Finally, \cite[Theorem 6]{Theory1} shows that the MSR3 relaxation is consistent with respect to the barrier, so that as the MSR3 parameter $\eta \uparrow \infty$,
 limit points of global solutions to the former are global solutions to the latter. 
 However, in the applications considered here,
 the empirical studies in Sections \ref{sec:synthetic} and \ref{sec:real}
 indicate that one does not need to make $\eta$ particularly large in order to accurately identify the correct sparsity pattern.

@@

\verify{Ensure that short and long performance tables are consistent with each other}
\begin{table}
\centering
\input{tables/performance_table_short_current}
\caption{\label{table:comparison_of_algorithms} Comparison of performance of algorithms measured as accuracy of selecting the correct covariates and run-time. The L0 strategy stands out 
over other standard regularizers. MSR3 improves performance significantly for all regularizers, while MSR3-fast improves convergence speed while preserving the 
accuracy of MSR3.  
More detailed results are in the Table \ref{table:detailed_comparison_of_algorithms} of Appendix \ref{appendix:detailed_comparison}.}
\end{table}

@@

\vskip -.8in
\begin{figure}
\center
		\includegraphics[width=9.5cm]{figures/eta_L1.pdf}
		\caption{Dependence of model performance on the relaxation $\eta$ for a sample problem.}\label{fig:eta}
\end{figure}

@@

\section{Theoretical Analysis}
\input{msr3-theory}

\section{Software Implementation}
\edit{Move pysr3 software paper here}
To ensure reproducibility of this research, all new algorithms have been implemented as a part of the \texttt{pysr3}\footnote{Available at \href{https://github.com/aksholokhov/pysr3}{https://github.com/aksholokhov/pysr3}} library~\cite{sholokhov2023pysr3}. This library implements functionality for fitting linear mixed models and selecting covariates. The user interface was designed to be fully compliant with the standards\footnote{\href{https://scikit-learn.org/stable/developers/develop.html}{https://scikit-learn.org/stable/developers/develop.html}} of \texttt{sklearn} library to minimize learning time.

The baseline optimization method of PySR3 is proximal gradient descent (PGD). Each regularizer included in PySR3 can also be used in its relaxed SR3 form. More information about the structure of the library can be found in documentation\footnote{https://aksholokhov.github.io/pysr3/},

>>>>

% \edit{Rewrite the MSR3 abstract into a summary of whole work with citations}
\paragraph{Abstract for Chapter~\ref{ch:msr3}} Linear Mixed-Effects (LME) models are a fundamental tool for modeling correlated data, 
including cohort studies, longitudinal data analysis, and meta-analysis.  Design and analysis of variable selection methods for LMEs is more difficult than for linear regression because LME models are nonlinear. In this work we 
propose a relaxation strategy and optimization methods that enable a wide range of variable selection methods for LMEs using both convex and nonconvex regularizers, including  $\ell_1$, Adaptive-$\ell_1$, SCAD, and $\ell_0$. 
The computational framework only requires the proximal operator for each regularizer to be available, and the implementation is available in an open source \texttt{python} package \texttt{pysr3}, consistent 
with the \texttt{sklearn} standard. 
The numerical results on simulated data sets indicate that the proposed strategy improves on the state of the art for both accuracy and compute time. 
The variable selection techniques are also validated on a real example using a data set on bullying victimization.

@@

%Roadmap
We begin in Section \ref{sec:LMEM} by giving a precise description of the LME
model and set the notation for the remainder of the paper. 
This is followed by a brief discussion of prior work on LMEs.
In Section \ref{sec:pgd_methods} we present our algorithms for the LME model 
starting with the naive PGD algorithm. This is followed by a description of the 
variable splitting technique used in \cite{Zheng2019SR3} to incorporate global 
variation information on the likelihood function into the direction finding subproblem
for the PGD algorithm. 
%This lays the foundation for the MSR3 algorithm. 
Next we tackle the problem of how to approximate the 
resulting optimal value function $u_\eta$ and its gradient where $\eta>0$ is the 
decoupling parameter. As noted, this is done using variable metric techniques and 
and interior point technology. We conclude Section \ref{sec:pgd_methods} 
with a discussion of the
MSR3 and MSR3-fast algorithms. In Section \ref{sec:applications} we discuss how
the underlying algorithmic parameters are set and test the algorithm on both 
simulated problems and a problem with real data. In Section~\ref{sec:theory-paper} we develop theoretical underpinnings of the proposed extension, including consistency results, variational properties, implementability of optimization methods, and convergence results for both MSR3 and MSR3-fast. Section~\ref{sec:software-paper} outlines the software implementation of MSR3 and MSR3-fast in \texttt{pysr3} package. The chapter is concluded in Section \ref{sec:discussion} with a brief discussion of the contributions.

@@

The individual random effects $u_i$ can be found through the minimization of conditional likelihood of random effects given $\beta$ and $\Gamma$:

\eq{
\min_{u_i}\LL(u_i|\beta, \Gamma) = \min_{u_i}\left(\half u_i^T\Gamma^{-1}u_i + \half (Z_iu_i - Y_i + F_i(\beta))^T\Lambda_i^{-1}(Z_iu_i - Y_i + F_i(\beta))\right),
}

This problem has a closed form solution commonly known as Best Linear Unbiased Predictor, or BLUP. It was first derived by \cite{Harville1976} as an extension to Gauss-Markov theorem.

 \eq{
	\label{eq:random_effects_formula}
	u_i = (\Gamma^{-1} + Z_i^T\Lambda_i^{-1}Z_i)^{-1}Z_i^T\Lambda_i^{-1}(Y_i - X_i\beta).	
}

@@

 A popular nonconvex regularizer used for feature selection is smoothed clipped absolute deviation (SCAD)~\cite{Fan2001}. 
 %The (non-smoothed) clipped absolute deviation penalty is depicted in panel (d) of Figure~\ref{fig:regularizers}.
% , and the algebraic forms for both CAD and SCAD are given in the appendix. 
% which acts on the first derivative of the penalty function $p_\lambda(\theta)$:
 %  \eq{
  % 		p'_{\lambda}(|\theta|) = \lambda\left\{\ind{\theta \leq \lambda} +  \frac{(a\lambda - \theta)_+}{(a-1)\lambda}\ind{\theta - \lambda} \right\}
  % }
The adaptation of the SCAD penalty to select both fixed and random features in 
linear mixed models was developed by \cite{Fan2012}. SCAD was also used by \cite{chen2015inference} for selecting fixed effects and establishing the existence of random effects in ANOVA-type models. Finally, \cite{Ghosh2018} studied SCAD regularization for selecting mean effects in high-dimensional genomics problems. One can refer to \cite{Muller2013, Buscemi2019Survey} for a detailed overview of different feature selection approaches.

To better compare methods, we need to consider the tuning of the regularization parameter 
$\lambda$. 
The output of a shrinkage model critically depends on the tuning parameter 
$\lambda$. The entire range of $\lambda$ values is captured 
by the notion of a ``$\lambda$-path in the model space'', with  the best parameter and the final model chosen using information criteria. According to \cite{Muller2013}, the most widely used information criterion is the marginal AIC criterion (\cite{Vaida2005}),
 \(  AIC := 2\LL(\hat{\theta}) + 2\alpha_n(p+q)\), 
  where $\hat\theta$ includes all the estimated parameters $(\beta, \Gamma)$, and $\alpha_n := n(n-p-q-1)$ for the finite sample case (\cite{Sugiura1978}). 
  %As discussed by \cite{Fang2011}, AIC is asymptotically equivalent to leave-one-out cross-validation, so it can be used for choosing between a finite number of models. AIC, however, is also known to be positively-biased (\cite{Ibrahim2011}). 
  Alternatively, LASSO-type methods (\cite{Krishna2008, Ibrahim2011}) use a BIC-type information criterion,  \(BIC := 2\LL(\hat{\theta}) + \log(n)(p+q)\).
BIC performs well in practice, but does not have theoretical guarantees~(\cite{schelldorfer2011estimation}). Finally, \cite{Hui2017} suggests penalizing the number of non-zero random effects in the resulting model instead of penalizing the number of random features with non-zero variance, especially when random effects are optimized directly instead of using BLUP~\eqref{eq:random_effects_formula}.

@@

Our focus is on the optimal value function $\uemu$ which captures global 
variational information about the function $\LL$ over its domain.
In Section~\ref{sec:theory-paper} we show that $\uemu$ has a locally Lipschitz continuous gradient
and that the evaluation of $\uemu$ and $\nabla \uemu$ is accomplished
by optimizing a well conditioned strongly convex function. This
allows us to apply the PGD algorithm to the function $\uemu$ rather than
the function $\LL$. Our numerical studies in Section~\ref{sec:applications} show that the global information 
captured by $\uemu$ significantly improves both the accuracy of the solution
obtained and the overall numerical efficiency of the algorithm.

@@

\begin{table}
\centering
\input{tables/performance_table_short_current}
\caption{\label{table:comparison_of_algorithms} Comparison of performance of algorithms measured as accuracy of selecting the correct covariates and run-time. The L0 strategy stands out 
over other standard regularizers. MSR3 improves performance significantly for all regularizers, while MSR3-fast improves convergence speed while preserving the 
accuracy of MSR3.  
More detailed results are in the Table \ref{table:detailed_comparison_of_algorithms} of Appendix \ref{appendix:detailed_comparison}.}
\end{table}

@@

\begin{figure}
\center
		\includegraphics[width=9.5cm]{figures/eta_L1.pdf}
		\caption{Dependence of model performance on the relaxation $\eta$ for a sample problem.}\label{fig:eta}
\end{figure}

@@

\section{Theoretical Analysis}
\label{sec:theory-paper}
\input{msr3-theory}

\section{Software Implementation}
\label{sec:software-paper}
To ensure reproducibility of this research, all new algorithms have been implemented as a part of the \texttt{pysr3}\footnote{Available at \href{https://github.com/aksholokhov/pysr3}{https://github.com/aksholokhov/pysr3}} library~(\cite{sholokhov2023pysr3}). This library implements functionality for fitting linear mixed models and selecting covariates. The user interface was designed to be fully compliant with the standards\footnote{\href{https://scikit-learn.org/stable/developers/develop.html}{https://scikit-learn.org/stable/developers/develop.html}} of \texttt{sklearn} library to minimize learning time.

The baseline optimization method of PySR3 is proximal gradient descent (PGD). Each regularizer included in PySR3 can also be used in its relaxed SR3 form. More information about the structure of the library can be found in the documentation\footnote{https://aksholokhov.github.io/pysr3/} as well as in the package's companion paper~(\cite{sholokhov2023pysr3}).
